H~3~: Issue area

### 2023-09-08 notebook/results-branding.qmd
Move labeling functions to targets
Better hypothesis icons
Update H1, H2, and H3 with new brms models

```{r libraries-data, warning=FALSE, message=FALSE}
library(tidyverse)
library(targets)
library(tidybayes)
library(patchwork)
library(scales)
library(glue)
library(gt)
library(gtExtras)
library(here)

# Helpful functions
label_pp <- label_number(accuracy = 1, scale = 100, 
  suffix = " pp.", style_negative = "minus")

fmt_decimal <- label_number(accuracy = 0.001, style_negative = "minus")

# Targets stuff
tar_config_set(store = here('_targets'),
               script = here('_targets.R'))

tar_load(c(means_features_only))

@@

::: {.callout-tip}
## H~1~: Branding

@@

```{r h1-calc-estimands}
h1_mms <- means_features_only %>% 
  group_by(feat_org, .draw) %>% 
  summarize(avg = mean(.epred))

@@

p_h1_amces <- h1_amces %>% 
  ungroup() %>% 
    separate_wider_delim(
    feat_org,
    delim = " - ", 
    names = c("feat_org", "reference_level")
  ) %>% 
  add_row(avg = 0, feat_org = "Amnesty International") %>% 
  ggplot(aes(x = avg, y = feat_org, fill = feat_org)) +
  stat_halfeye() +
  geom_vline(xintercept = 0, color = clrs$prism[8], linetype = "dashed", linewidth = 0.25) +
  scale_x_continuous(labels = label_pp) +
  scale_y_discrete(labels = label_wrap(10)) +
  scale_fill_manual(values = clrs$prism[c(1, 3, 5, 7)], guide = "none") +
  labs(
    x = "Percentage point change in probability of choice selection",
    y = NULL,
    fill = NULL,
    title = "Average marginal component effects (AMCEs)"
  )

>>>>

```{r libraries-data, warning=FALSE, message=FALSE}
library(tidyverse)
library(targets)
library(tidybayes)
library(patchwork)
library(scales)
library(glue)
library(gt)
library(gtExtras)

# Targets stuff
tar_config_set(
  store = here::here("_targets"),
  script = here::here("_targets.R")
)

preds_all <- tar_read(preds_conditional_treatment_only)

@@

::: {.callout-tip icon=false}
## {{< iconify fa6-solid flask-vial >}} Hypothesis 1: Branding

@@

```{r h1-calc-estimands}
h1_mms <- preds_all %>% 
  group_by(feat_org, .draw) %>% 
  summarize(avg = mean(.epred))

@@

p_h1_amces <- h1_amces %>% 
  ungroup() %>% 
    separate_wider_delim(
    feat_org,
    delim = " - ", 
    names = c("feat_org", "reference_level")
  ) %>% 
  add_row(avg = 0, feat_org = unique(.$reference_level)) %>% 
  ggplot(aes(x = avg, y = feat_org, fill = feat_org)) +
  stat_halfeye() +
  geom_vline(xintercept = 0, color = clrs$prism[8], linetype = "dashed", linewidth = 0.25) +
  scale_x_continuous(labels = label_pp) +
  scale_y_discrete(labels = label_wrap(10)) +
  scale_fill_manual(values = clrs$prism[c(1, 3, 5, 7)], guide = "none") +
  labs(
    x = "Percentage point change in probability of choice selection",
    y = NULL,
    fill = NULL,
    title = "Average marginal component effects (AMCEs)"
  )

### 2023-09-08 notebook/results-crackdown.qmd
Update H1, H2, and H3 with new brms models

```{r libraries-data, warning=FALSE, message=FALSE}
library(tidyverse)
library(targets)
library(tidybayes)
library(patchwork)
library(scales)
library(glue)
library(gt)
library(gtExtras)
library(here)

# Targets stuff
tar_config_set(store = here('_targets'),
               script = here('_targets.R'))

tar_load(c(means_features_only))

@@

```{r h2a-calc-estimands}
h2a_mms <- means_features_only %>% 
  group_by(feat_govt, .draw) %>% 
  summarize(avg = mean(.epred))

@@

p_h2a_amces <- h2a_amces %>% 
  ungroup() %>% 
  separate_wider_delim(
    feat_govt,
    delim = " - ", 
    names = c("feat_govt", "reference_level")
  ) %>% 
  add_row(avg = 0, feat_govt = "Friendly") %>%
  mutate(feat_govt = factor(feat_govt, levels = levels(h2a_mms$feat_govt))) %>% 
  ggplot(aes(x = avg, y = feat_govt, fill = feat_govt)) +
  stat_halfeye() +
  geom_vline(xintercept = 0, color = clrs$prism[8], linetype = "dashed", linewidth = 0.25) +
  scale_x_continuous(labels = label_pp) +
  scale_y_discrete(labels = label_wrap(10)) +
  scale_fill_manual(values = clrs$peach[c(2, 5, 7)], guide = "none") +
  labs(
    x = "Percentage point change in probability of choice selection",
    y = NULL,
    fill = NULL,
    title = "Average marginal component effects (AMCEs)"
  )

@@

```{r h2b-calc-estimands}
h2b_mms <- means_features_only %>% 
  mutate(org_collapsed = fct_collapse(feat_org, 
    `Oxfam & Red Cross` = c("Oxfam", "Red Cross"),
    `Amnesty International & Greenpeace` = c("Amnesty International", "Greenpeace"))) %>% 
  group_by(org_collapsed, feat_govt, .draw) %>% 
  summarize(avg = mean(.epred))

>>>>

```{r libraries-data, warning=FALSE, message=FALSE}
library(tidyverse)
library(targets)
library(tidybayes)
library(patchwork)
library(scales)
library(glue)
library(gt)
library(gtExtras)

tar_config_set(
  store = here::here("_targets"),
  script = here::here("_targets.R")
)

preds_all <- tar_read(preds_new_treatment_only)

@@

```{r h2a-calc-estimands}
h2a_mms <- preds_all %>% 
  group_by(feat_govt, .draw) %>% 
  summarize(avg = mean(.epred))

@@

p_h2a_amces <- h2a_amces %>% 
  ungroup() %>% 
  separate_wider_delim(
    feat_govt,
    delim = " - ", 
    names = c("feat_govt", "reference_level")
  ) %>% 
  add_row(avg = 0, feat_govt = unique(.$reference_level)) %>%
  mutate(feat_govt = factor(feat_govt, levels = levels(h2a_mms$feat_govt))) %>% 
  ggplot(aes(x = avg, y = feat_govt, fill = feat_govt)) +
  stat_halfeye() +
  geom_vline(xintercept = 0, color = clrs$prism[8], linetype = "dashed", linewidth = 0.25) +
  scale_x_continuous(labels = label_pp) +
  scale_y_discrete(labels = label_wrap(10)) +
  scale_fill_manual(values = clrs$peach[c(2, 5, 7)], guide = "none") +
  labs(
    x = "Percentage point change in probability of choice selection",
    y = NULL,
    fill = NULL,
    title = "Average marginal component effects (AMCEs)"
  )

@@

```{r h2b-calc-estimands}
h2b_mms <- preds_all %>% 
  mutate(org_collapsed = fct_collapse(feat_org, 
    `Oxfam & Red Cross` = c("Oxfam", "Red Cross"),
    `Amnesty International & Greenpeace` = c("Amnesty International", "Greenpeace"))) %>% 
  group_by(org_collapsed, feat_govt, .draw) %>% 
  summarize(avg = mean(.epred))

### 2023-09-08 notebook/results-issue.qmd
Update H1, H2, and H3 with new brms models

```{r libraries-data, warning=FALSE, message=FALSE}
library(tidyverse)
library(targets)
library(tidybayes)
library(patchwork)
library(scales)
library(glue)
library(gt)
library(gtExtras)
library(here)

# Targets stuff
tar_config_set(store = here('_targets'),
               script = here('_targets.R'))

tar_load(c(means_features_only))

@@

```{r h3a-calc-estimands}
h3a_mms <- means_features_only %>% 
  group_by(feat_issue, .draw) %>% 
  summarize(avg = mean(.epred))

@@

p_h3a_amces <- h3a_amces %>% 
  ungroup() %>% 
  separate_wider_delim(
    feat_issue,
    delim = " - ", 
    names = c("feat_issue", "reference_level")
  ) %>% 
  add_row(avg = 0, feat_issue = "Emergency response") %>%
  mutate(feat_issue = factor(feat_issue, levels = levels(h3a_mms$feat_issue))) %>% 
  ggplot(aes(x = avg, y = feat_issue, fill = feat_issue)) +
  stat_halfeye() +
  geom_vline(xintercept = 0, color = clrs$prism[8], linetype = "dashed", linewidth = 0.25) +
  scale_x_continuous(labels = label_pp) +
  scale_y_discrete(labels = label_wrap(10)) +
  scale_fill_manual(values = clrs$prism[c(2, 6, 8, 10)], guide = "none") +
  labs(
    x = "Percentage point change in probability of choice selection",
    y = NULL,
    fill = NULL,
    title = "Average marginal component effects (AMCEs)"
  )

@@

```{r h3b-calc-estimands}
h3b_mms <- means_features_only %>% 
  group_by(feat_issue, feat_govt, .draw) %>% 
  summarize(avg = mean(.epred))

@@

p_h3b_amces <- h3b_amces %>% 
  ungroup() %>% 
  separate_wider_delim(
    feat_issue,
    delim = " - ", 
    names = c("feat_issue", "reference_level")
  ) %>% 
  add_row(avg = 0, feat_issue = "Emergency response", feat_govt = "Friendly") %>%
  add_row(avg = 0, feat_issue = "Emergency response", feat_govt = "Criticized") %>%
  add_row(avg = 0, feat_issue = "Emergency response", feat_govt = "Under crackdown") %>%
  mutate(feat_issue = factor(feat_issue, levels = levels(h3b_mms$feat_issue))) %>% 
  ggplot(aes(x = avg, y = feat_issue, fill = feat_issue)) +
  stat_halfeye() +
  geom_vline(xintercept = 0, color = clrs$prism[8], linetype = "dashed", linewidth = 0.25) +
  scale_x_continuous(labels = label_pp) +
  scale_y_discrete(labels = label_wrap(10)) +
  scale_fill_manual(values = clrs$prism[c(2, 6, 8, 10)], guide = "none") +
  facet_wrap(vars(feat_govt), ncol = 1) +
  labs(
    x = "Percentage point change in probability of choice selection",
    y = NULL,
    fill = NULL,
    title = "Difference in estimated marginal means"
  )

>>>>

```{r libraries-data, warning=FALSE, message=FALSE}
library(tidyverse)
library(targets)
library(tidybayes)
library(patchwork)
library(scales)
library(glue)
library(gt)
library(gtExtras)

tar_config_set(
  store = here::here("_targets"),
  script = here::here("_targets.R")
)

preds_all <- tar_read(preds_conditional_treatment_only)

@@

```{r h3a-calc-estimands}
h3a_mms <- preds_all %>% 
  group_by(feat_issue, .draw) %>% 
  summarize(avg = mean(.epred))

@@

p_h3a_amces <- h3a_amces %>% 
  ungroup() %>% 
  separate_wider_delim(
    feat_issue,
    delim = " - ", 
    names = c("feat_issue", "reference_level")
  ) %>% 
  add_row(avg = 0, feat_issue = unique(.$reference_level)) %>%
  mutate(feat_issue = factor(feat_issue, levels = levels(h3a_mms$feat_issue))) %>% 
  ggplot(aes(x = avg, y = feat_issue, fill = feat_issue)) +
  stat_halfeye() +
  geom_vline(xintercept = 0, color = clrs$prism[8], linetype = "dashed", linewidth = 0.25) +
  scale_x_continuous(labels = label_pp) +
  scale_y_discrete(labels = label_wrap(10)) +
  scale_fill_manual(values = clrs$prism[c(2, 6, 8, 10)], guide = "none") +
  labs(
    x = "Percentage point change in probability of choice selection",
    y = NULL,
    fill = NULL,
    title = "Average marginal component effects (AMCEs)"
  )

@@

```{r h3b-calc-estimands}
h3b_mms <- preds_all %>% 
  group_by(feat_issue, feat_govt, .draw) %>% 
  summarize(avg = mean(.epred))

@@

p_h3b_amces <- h3b_amces %>% 
  ungroup() %>% 
  separate_wider_delim(
    feat_issue,
    delim = " - ", 
    names = c("feat_issue", "reference_level")
  ) %>% 
  add_row(avg = 0, feat_issue = "Emergency response", feat_govt = "Friendly relationship with government") %>%
  add_row(avg = 0, feat_issue = "Emergency response", feat_govt = "Criticized by government") %>%
  add_row(avg = 0, feat_issue = "Emergency response", feat_govt = "Under government crackdown") %>%
  mutate(feat_issue = factor(feat_issue, levels = levels(h3b_mms$feat_issue))) %>% 
  ggplot(aes(x = avg, y = feat_issue, fill = feat_issue)) +
  stat_halfeye() +
  geom_vline(xintercept = 0, color = clrs$prism[8], linetype = "dashed", linewidth = 0.25) +
  scale_x_continuous(labels = label_pp) +
  scale_y_discrete(labels = label_wrap(10)) +
  scale_fill_manual(values = clrs$prism[c(2, 6, 8, 10)], guide = "none") +
  facet_wrap(vars(feat_govt), ncol = 1) +
  labs(
    x = "Percentage point change in probability of choice selection",
    y = NULL,
    fill = NULL,
    title = "Difference in estimated marginal means"
  )
